### 2021-04-16 notes/erf_setup/erf_cartesian_setup.tex
updates model setup pdf with P -> 1/P change

\section{Model Setup}
We will study a two-layer model in $z = [0, L_z]$ in which the conductivity, $k(z)$ is a step function such that
\begin{equation}
k(z) = \begin{cases}
k_b & z < 1 \\
k_t & z \geq 1
\end{cases}
\end{equation}
where subscript ``t'' refers to the top layer and ``b'' refers to the bottom.
(These won't be true discontinuities, but will be smooth step-like functions achieved with erfs.)

There will be two important input parameters in this system:
\begin{enumerate}
\item The stiffness, 
\begin{equation}
\mathcal{S} = \frac{N_{t}^2}{f_{\mathrm{conv}}^2},
\end{equation}
which is the ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
\item $\mathcal{P}$, a parameter which determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
We will define $\mathcal{P} = -F_{\rm{conv, rz}}/F_{\rm{conv}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \ll 1$ and none when $\mathcal{P} \gg 1$.
\end{enumerate}
In addition to these parameters, the magnitude of the heating, $Q$ and the vertical extent of the heating layer, $\delta_H$, must be specified as they set $F_{\rm{conv}} = Q \delta_H$.
We will choose $Q = 1$ and $\delta_H = 0.2$ so that $F_{\rm{conv}} = 0.2$; we will furthermore choose and $F_{\rm{bot}} = \zeta F_{\rm{conv}}$, where $\zeta$ is some arbitrary scalar that sets how much smaller $k$ is in the cz than the RZ; we'll set $\zeta = 10^{-3}$ for now.

Under these choices, the system is determined by five equations,
\begin{enumerate}
\item At some point, the adiabatic gradient is equal to the radiative gradient,
\begin{equation}
k_{\rm{ad}}\grad_{\rm{ad}} = F_{\rm{tot}}.
\end{equation}
\item at $z = 0$, the base of the CZ, the adiabatic temperature gradient is the radiative gradient, $\grad_{\rm{ad}} = \grad_{\rm{rad}}$, and carries $F_{\rm{bot}}$,
\begin{equation}
k_b \grad_{\rm{ad}} = F_{\rm{bot}}
\end{equation}
\item The radiative gradient can carry the flux in the RZ,
\begin{equation}
k_{t} \grad_{\rm{rad,t}} = F_{\rm{tot}}
\end{equation}
\item Assuming $\grad T = -\grad_{\rm{ad}}$ everywhere, the convective flux in the top layer is $F_{\rm{conv,t}} = F_{\rm{conv}} - \Delta k \grad_{\rm{ad}}$, where $F_{\rm{conv}} = Q \delta_H$ and $\Delta k = k_t - k_b$.
Thus, definitionally,
\begin{equation}
\mathcal{P} = -\frac{F_{\rm{conv,t}}}{F_{\rm{conv}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right).
\end{equation}
\item Defining $f_{\rm{conv}}^2 \approx Q$ and $N^2 \approx -(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})$, the stiffness gives
\begin{equation}
\mathcal{S} = \frac{N^2}{f_{\mathrm{conv}}^2} = \frac{-(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})}{Q}
= \frac{F_{\mathrm{tot}}}{Q}(k_{\rm{ad}}^{-1} - k_t^{-1})
\end{equation}
\end{enumerate}

Solving this system of equations gives
\begin{align}
k_t = \frac{\delta_H \mathcal{P}}{\mathcal{S}},\qquad
k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}},\qquad
k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}},\\
\grad_{\rm{ad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta + \mathcal{P}),\qquad
\grad_{\rm{rad}} = \frac{Q \mathcal{S}}{\mathcal{P}}(1 + \zeta).
\end{align}

>>>>

\section{Model Setup}
We will study a two-layer model in $z = [0, L_z]$ in which the conductivity, $k(z)$ is a step function such that
\begin{equation}
k(z) = \begin{cases}
k_b & z < L_{\rm{cz}} \\
k_t & z \geq L_{\rm{cz}}
\end{cases}
\end{equation}
where subscript ``t'' refers to the top layer and ``b'' refers to the bottom.
Generally, we will set $L_{\rm{cz}} = 1$.
(These won't be true discontinuities, but will be smooth step-like functions achieved with erfs.)

There will be two important input parameters in this system:
\begin{enumerate}
\item The stiffness, 
\begin{equation}
\mathcal{S} = \frac{N_{t}^2}{f_{\mathrm{conv}}^2},
\end{equation}
which is the ratio of the buoyancy frequency (in the stable layer) to the square convective frequency.
\item $\mathcal{P}$, a parameter which sets the penetration depth.
$\mathcal{P}$ determines what the magnitude of the \emph{negative} convective flux would be in an adiabatic penetrative layer with $k = k_t$.
We will define $\mathcal{P} = -F_{\rm{conv}}/F_{\rm{conv, rz}}$, and our expectation is that we get a lot of convective penetration when $\mathcal{P} \gg 1$ and none when $\mathcal{P} \ll 1$.
\end{enumerate}
In addition to these parameters, the magnitude of the heating, $Q$ and the vertical extent of the heating layer, $\delta_H$, must be specified as they set $F_{\rm{conv}} = Q \delta_H$.
We will choose $Q = 1$ and $\delta_H = 0.2$ so that $F_{\rm{conv}} = 0.2$; we will furthermore choose and $F_{\rm{bot}} = \zeta F_{\rm{conv}}$, where $\zeta$ is some arbitrary scalar that sets how much smaller $k$ is in the cz than the RZ; we'll set $\zeta = 10^{-3}$ for now.

Under these choices, the system is determined by five equations,
\begin{enumerate}
\item At some point, the adiabatic gradient is equal to the radiative gradient,
\begin{equation}
k_{\rm{ad}}\grad_{\rm{ad}} = F_{\rm{tot}}.
\end{equation}
\item at $z = 0$, the base of the CZ, the adiabatic temperature gradient is the radiative gradient, $\grad_{\rm{ad}} = \grad_{\rm{rad}}$, and carries $F_{\rm{bot}}$,
\begin{equation}
k_b \grad_{\rm{ad}} = F_{\rm{bot}}
\end{equation}
\item The radiative gradient can carry the flux in the RZ,
\begin{equation}
k_{t} \grad_{\rm{rad,t}} = F_{\rm{tot}}
\end{equation}
\item Assuming $\grad T = -\grad_{\rm{ad}}$ everywhere, the convective flux in the top layer is $F_{\rm{conv,t}} = F_{\rm{conv}} - \Delta k \grad_{\rm{ad}}$, where $F_{\rm{conv}} = Q \delta_H$ and $\Delta k = k_t - k_b$.
Thus, definitionally,
\begin{equation}
\mathcal{P} = -\frac{F_{\rm{conv}}}{F_{\rm{conv,t}}} = \left(\frac{\Delta k \grad_{\rm{ad}}}{Q \delta_H} - 1\right)^{-1}.
\end{equation}
\item Defining $f_{\rm{conv}}^2 \approx Q$ and $N^2 \approx -(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})$, the stiffness gives
\begin{equation}
\mathcal{S} = \frac{N^2}{f_{\mathrm{conv}}^2} = \frac{-(\grad_{\rm{rad,t}} - \grad_{\rm{ad}})}{Q}
= \frac{F_{\mathrm{tot}}}{Q}(k_{\rm{ad}}^{-1} - k_t^{-1})
\end{equation}
\end{enumerate}

Solving this system of equations gives
\begin{align}
k_t = \frac{\delta_H}{\mathcal{S} \mathcal{P}},\qquad
k_b = k_t \frac{\zeta}{1 + \zeta + \mathcal{P}^{-1}},\qquad
k_{\rm{ad}} = k_t \frac{1 + \zeta}{1 + \zeta + \mathcal{P}^{-1}},\\
\grad_{\rm{ad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta + \mathcal{P}^{-1}),\qquad
\grad_{\rm{rad}} = Q \mathcal{S}\mathcal{P}(1 + \zeta).
\end{align}
